Growing Up With Nell: A Narrative Interface for Literacy

### 2012-04-24 paper.tex
"beginning" -> "starting" to fix an overfull hbox.

\section{Conclusions}
We have described the design of a novel narrative direct-interface
system for education, beginning with literacy, which is personalized for and grows with
its child owner.  Personalized direct interface engages the child, and
narrative guides them through pedagogic material.  Low-cost
solar-powered hardware allows Nell to reach further into the
least-developed areas of the world to help those without traditional
educational infrastructure.

>>>>

\section{Conclusions}
We have described the design of a novel narrative direct-interface
system for education, starting with literacy, which is personalized for and grows with
its child owner.  Personalized direct interface engages the child, and
narrative guides them through pedagogic material.  Low-cost
solar-powered hardware allows Nell to reach further into the
least-developed areas of the world to help those without traditional
educational infrastructure.
